Using Fundamental Measure Theory to Treat the Correlation Function of the Inhomogeneous Hard-Sphere Fluid

### 2012-12-12 papers/contact/paper.tex
Another big edit after third referee response.  Added svg figures and changed some text in paper Eq 17,18,24 Tested everything on kipu.

%\pacs{61.20.Ne, 61.20.Gy, 61.20.Ja}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
  We investigate the value of the correlation function of an
  inhomogeneous hard-sphere fluid at contact.  This
  quantity plays a critical role in Statistical Associating Fluid
  Theory (SAFT), which is the basis of a number of recently developed classical
  density functionals.  We define two averaged values for the
  correlation function at contact, and derive formulas for each of
  them from the White Bear version of the Fundamental Measure Theory
  functional~\cite{roth2002whitebear}, using an assumption of
  thermodynamic consistency. We test these formulas, as well as two
  existing formulas~\cite{yu2002fmt-dft-inhomogeneous-associating,
    gross2009density} against Monte Carlo simulations, and find
  excellent agreement between the Monte Carlo data and one of our
  averaged correlation functions.
\end{abstract}

@@

In order to motivate our derivation of the correlation function at
contact for the \emph{inhomogeneous} hard-sphere fluid, we begin by
deriving the well-known formula for $g_\sigma$ for the
\emph{homogeneous} fluid that comes from the Carnahan-Starling free
energy.  The contact value of the correlation function density can be
found by using the contact-value theorem, which states that the
pressure on any hard surface is determined by the density at contact:
\begin{align}
  p(\rr_c) &= k_BT n(\rr_c)
\end{align}
where $\rr_c$ is a position of a sphere that would be in contact with
the hard surface, and $p(\rr_c)$ is the pressure that the spheres
exert on that surface at the point $\rr_c$.  This pressure is
understood as the ratio of force to an infinitesimal element of
\emph{solvent accessible surface} area.
%
In the homogeneous fluid, the contact-value theorem implies that
\begin{align}
  p &= k_BT n g_\sigma.
\end{align}
Since we are interested in the correlation function at the surface at
which hard spheres contact, we need to compute the pressure on that
surface.   This pressure can be
readily computed from the dependence of the Carnahan-Starling free
energy on hard sphere radius.
\begin{align}
  A_{HS} &= Nk_BT \frac{4\eta - 3\eta^2}{(1-\eta)^2}
\end{align}
where $\eta \equiv \frac{\pi}{6} \sigma^3 n$ is the filling fraction.
We compute the pressure on each sphere using the total force with
respect to a changing radius of all the spheres.
To find the pressure, we divide by $4\pi \sigma^2$, which is the area
over which contact is possible, as defined by the centers of the
contacting spheres, as illustrated in Figure~\ref{fig:nA}.
Finally, we divide by $N$ to account for the total area of all the
spheres in the fluid.
\begin{align}
  p_\sigma &= \frac{1}{N 4\pi \sigma^2} \frac{dA_{HS}}{dR} \\
  &= \frac{1}{N 4\pi \sigma^2} \frac12 \frac{dA_{HS}}{d\sigma} \\
  &= k_BT n \frac{1 - \frac{\eta}2}{(1-\eta)^3}
\end{align}
Using the contact-value theorem, we can thus find the well-known
correlation function evaluated at contact.
\begin{align}
  g_\sigma &= \frac{1 - \frac{\eta}2}{(1-\eta)^3} \label{eq:cs-g}
\end{align}
Extending this derivation to the inhomogeneous fluid requires that we
find the pressure felt by the surface of particular spheres.

@@

We will begin our derivation of the locally averaged correlation
function with the asymmetric definition of $g_\sigma^A(\rr)$ given in
Equation~\ref{eq:gA}, which is averaged over contacts in which one of
the two spheres is located at position~$\rr$.  This correlation
function is related to the contact density averaged over the surface
of a sphere located at~$\rr$, and can thus be determined by finding
the pressure on that sphere.  We find this pressure from the change in
free energy resulting from an infinitesimal expansion of any
spheres located at position~$\rr$.  From this pressure, we derive a
formula for the correlation function $g_\sigma^A(\rr)$ as was done in
the previous section:
\begin{align}
  p_\sigma(\mathbf{r}) &= \frac{1}{n(\rr) 4\pi \sigma^2}\frac12 \frac{\delta
    A_{HS}}{\delta \sigma(\mathbf{r})} \label{eq:p_{HS}^A}\\
%  \ncontact(\rr) &= \frac{1}{n(\rr) k_BT 4\pi \sigma^2}\frac12 \frac{\delta
%    A_{HS}}{\delta \sigma(\mathbf{r})} \\
  g_\sigma^A(\rr)% &= \frac{\ncontact(\rr)}{n_A(\rr)} \\
  &= \frac{1}{n(\rr) n_A(\rr)}\frac{1}{ k_BT 4\pi \sigma^2}\frac12 \frac{\delta
    A_{HS}}{\delta \sigma(\mathbf{r})} \label{eq:g-A-exact}
\end{align}
Equation~\ref{eq:g-A-exact} is an exact expression for
$g_\sigma^A(\rr)$ as defined in Equation~\ref{eq:gA}.  However, since
we do not know the exact hard-sphere free energy, we approximate
$A_{HS}$ using FMT.  Details of evaluating the functional derivative
in Equation~\ref{eq:g-A-exact} using FMT are given in the appendix.
The equation for $g_\sigma^A$ requires finding convolutions of local
derivatives of the free energy, making this formulation
computationally somewhat more expensive than the free energy itself.

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/walls-10}
  \caption{Density and correlation function at a hard wall with bulk
    filling fraction of 0.1.}
  \label{fig:walls-10}
\end{figure}

@@

We simulate the inhomogeneous hard sphere fluid at four hard-wall
interfaces.  The first and simplest is a flat hard wall.  We
then study two convex hard surfaces.  One is an excluded sphere with
diameter $2\sigma$, which corresponds to a ``test particle''
simulation with one of a hard sphere at the origin with diameter
$\sigma$.  The second is an excluded sphere with diameter $6\sigma$,
which demonstrates behavior typical of mildly convex hard surfaces.
Finally, we study a concave surface given by a hard cavity in which
our fluid is free to move up to a diameter of $16\sigma$, which
demonstrates behavior typical of mildly concave surfaces.  In each
case, we performed a low-density (filling fraction 0.1) and high-density
(filling fraction 0.4) simulation.  We performed additional
computations over a wider range of curvatures and densities, but
chose these as typical examples.

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/inner-4-10}
  \caption{Density and correlation function around a hard sphere with
    diameter the same as those in the fluid, with a bulk filling
    fraction of 0.1.}
  \label{fig:inner-4-10}
\end{figure}

@@

We begin by presenting our low-density results, corresponding to a
filling fraction of 0.1, which are shown in
Figures~\ref{fig:walls-10}-\ref{fig:outer-10}.  At this low density,
the contact value of the correlation function in the bulk is only 1.3,
indicating that correlations are indeed small and that the fluid should be
relatively easy to model.  Indeed, the contact density at the hard
surface is only around 50\% higher than the bulk, and the FMT
predicted density is close to indistinguishable from the true
density for each of the four configurations.

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/inner-12-10}
  \caption{Density and correlation function around a hard sphere with
    an excluded diameter of $6\sigma$, with a bulk filling fraction of
    0.1.}
  \label{fig:inner-12-10}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/outer-16-01}
  \caption{Density and correlation functions near the surface of a
    spherical cavity with diameter $16\sigma$ at a bulk filling
    fraction of 0.1.}
  \label{fig:outer-10}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/walls-40}
  \caption{Density and correlation function at a hard wall with bulk
    filling fraction of 0.4.}
  \label{fig:walls-40}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/inner-4-40}
  \caption{Density and correlation function around a hard sphere with
    diameter the same as those in the fluid, with a bulk filling
    fraction of 0.4.}
  \label{fig:inner-4-40}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/inner-12-40}
  \caption{Density and correlation function around a hard sphere with
    an excluded diameter of $6\sigma$, with a bulk filling fraction of
    0.4.}
  \label{fig:inner-12-40}
\end{figure}

At a higher density corresponding to a filling fraction of 0.4,
correlations are much stronger, with the bulk contact value of the
correlation function of 3.7, as seen in
Figures~\ref{fig:walls-40}-\ref{fig:outer-40}.  This results in larger
oscillations in the density at the hard surfaces, and correspondingly
more interesting behavior in the correlation function near the
interface.  The density predicted by the White Bear functional agrees
reasonably well with the simulation results, although not so well as
it did at lower density.  The discrepancies are largest in the case of
the spherical cavity, in which the DFT considerably underestimates the
range of the density oscillations.

The asymmetric version of the correlation function once again displays
relatively smooth behavior with a few small
oscillations near the interface, and a somewhat elevated value within
a diameter of the hard surface, with the magnitude of this elevation
somewhat different in each configuration.  As was the case at low
density, our correlation function $g_\sigma^A$ matches very closely
the Monte Carlo data, reproducing quite well the structure near the
interface in each configuration, although in the spherical cavity
(Figure~\ref{fig:outer-40}), there is a small, but significant
discrepancy, comparable to the discrepancy found in the density
itself.  In each case, the correlation of Gross dramatically
underestimates the correlation at the interface, at one extreme by
40\% in the case of the spherical cavity
(Figure~\ref{fig:outer-40}), and at the other extreme by 15\%
in the test-particle scenario (Figure~\ref{fig:inner-4-40}).

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/outer-16-04}
  \caption{Density and correlation functions near the surface of a
    spherical cavity with diameter $16\sigma$ at a bulk filling
    fraction of 0.4.}
  \label{fig:outer-40}
\end{figure}

The symmetrically averaged correlation function shows considerably
more structure near the interface at high density, and this structure
varies considerably depending on the curvature of the hard surface.
In each case, this structure is not reflected in the theoretical
predictions, neither that of this paper, nor that of Yu and
Wu~\cite{yu2002fmt-dft-inhomogeneous-associating}.  As was the case at
low density, both functionals give significant and finite values in
the region in which there are no contacts, but at high density they
also miss the large oscillations that are present near the flat wall
and the concave surface (Figures~\ref{fig:walls-40}
and~\ref{fig:outer-40}).  As was the case at low density, the
functional of Yu and Wu~\cite{yu2002fmt-dft-inhomogeneous-associating}
gives slightly better agreement with the simulation results than that
which we derive in Section~\ref{sec:g-S}.

>>>>

%\pacs{61.20.Ne, 61.20.Gy, 61.20.Ja}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
  We investigate the value of the correlation function of an
  inhomogeneous hard-sphere fluid at contact.  This
  quantity plays a critical role in Statistical Associating Fluid
  Theory (SAFT), which is the basis of a number of recently developed classical
  density functionals.  We define two averaged values for the
  correlation function at contact, and derive formulas for each of
  them from the White Bear version of the Fundamental Measure Theory
  functional, using an assumption of
  thermodynamic consistency. We test these formulas, as well as two
  existing formulas against Monte Carlo simulations, and find
  excellent agreement between the Monte Carlo data and one of our
  averaged correlation functions.
\end{abstract}

@@

In order to motivate our derivation of the correlation function at
contact for the \emph{inhomogeneous} hard-sphere fluid, we begin by
deriving the well-known formula for $g_\sigma$ for the
\emph{homogeneous} fluid that comes from the Carnahan-Starling free
energy.  The contact value of the correlation function density can be
found by using the contact-value theorem, which states that the
pressure on any hard surface is determined by the density at contact:
\begin{align}
  p(\rr_c) &= k_BT n(\rr_c)
\end{align}
where $\rr_c$ is a position of a sphere that would be in contact with
the hard surface, $n(\rr_c)$ is the density at this point $\rr_c$, and $p(\rr_c)$ is the pressure that the spheres
exert on the surface at the same point.  This pressure is
understood as the ratio of force to an infinitesimal element of
\emph{solvent accessible surface} (SAS) area.
%
In the homogeneous fluid, the contact-value theorem implies that
\begin{align}
  p_{\textit{SAS}} &= k_BT n g_\sigma
\end{align}
where $p_{SAS}$ is the pressure on a hard sphere's solvent accessible surface.
This pressure can be
readily computed from the dependence of the Carnahan-Starling free
energy on hard sphere radius:
\begin{align}
  A_{HS} &= Nk_BT \frac{4\eta - 3\eta^2}{(1-\eta)^2}
\end{align}
where $\eta \equiv \frac{\pi}{6} \sigma^3 n$ is the filling fraction.
We compute the pressure using the total force with
respect to a changing radius of all the spheres.
To find the pressure, we divide this force by $4\pi \sigma^2$, which
is the SAS area of a single hard sphere, illustrated in Figure~\ref{fig:nA}.
Finally, we divide by $N$ to account for the total area of all the
spheres in the fluid.
\begin{align}
  p_{\textit{SAS}} &= \frac{1}{N 4\pi \sigma^2} \frac{dA_{HS}}{dR} \\
  &= \frac{1}{N 4\pi \sigma^2} \frac12 \frac{dA_{HS}}{d\sigma} \\
  &= k_BT n \frac{1 - \frac{\eta}2}{(1-\eta)^3}
\end{align}
Using the contact-value theorem, we thus find the well-known
correlation function evaluated at contact.
\begin{align}
  g_\sigma &= \frac{1 - \frac{\eta}2}{(1-\eta)^3} \label{eq:cs-g}
\end{align}
Extending this derivation to the inhomogeneous fluid requires that we
find the pressure felt by the surface of particular spheres.

@@

We will begin our derivation of the locally averaged correlation
function with the asymmetric definition of $g_\sigma^A(\rr)$ given in
Equation~\ref{eq:gA}, which is averaged over contacts in which one of
the two spheres is located at position~$\rr$.  This correlation
function is related to the contact density averaged over the solvent accessible surface
of a sphere located at~$\rr$, and can thus be determined by finding
the pressure on that surface.  We find this pressure from the change in
free energy resulting from an infinitesimal expansion of spheres
located at position~$\rr$.  From this pressure, we derive a
formula for the correlation function $g_\sigma^A(\rr)$ as was done in
the previous section:
\begin{align}
  p_{\textit{SAS}}(\mathbf{r}) &= \frac{1}{n(\rr) 4\pi \sigma^2}\frac12 \frac{\delta
    A_{HS}}{\delta \sigma(\mathbf{r})} \label{eq:p_{HS}^A}\\
%  \ncontact(\rr) &= \frac{1}{n(\rr) k_BT 4\pi \sigma^2}\frac12 \frac{\delta
%    A_{HS}}{\delta \sigma(\mathbf{r})} \\
  g_\sigma^A(\rr)% &= \frac{\ncontact(\rr)}{n_A(\rr)} \\
  &= \frac{1}{n(\rr) n_A(\rr)}\frac{1}{ k_BT 4\pi \sigma^2}\frac12 \frac{\delta
    A_{HS}}{\delta \sigma(\mathbf{r})} \label{eq:g-A-exact}
\end{align}
where $\sigma(\mathbf{r})$ is the diameter of spheres located at position $\rr$.
Details regarding the evaluation of the functional derivative $\frac{\delta A_{HS}}{\delta \sigma(\mathbf{r})}$
are discussed in the Appendix.
Equation~\ref{eq:g-A-exact} is an exact expression for
$g_\sigma^A(\rr)$ as defined in Equation~\ref{eq:gA}.  However, since
we do not know the exact hard-sphere free energy, we approximate
$A_{HS}$ using FMT.  Details of evaluating the functional derivative
in Equation~\ref{eq:g-A-exact} using FMT are given in the appendix.
The equation for $g_\sigma^A$ requires finding convolutions of local
derivatives of the free energy, making this formulation
computationally somewhat more expensive than the free energy itself.

@@

%% \begin{figure}
%%   \includegraphics[width=\columnwidth]{figs/walls-10}
%%   \caption{Density and correlation function at a hard wall with bulk
%%     filling fraction of 0.1.  In the top and middle panels are plotted
%%     the asymmetrically averaged correlation function $g_\sigma^A$
%%     (defined in Equation~\ref{eq:gA}) and the symmetrically averaged
%%     correlation function $g_\sigma^S$ (defined in
%%     Equation~\ref{eq:gS}).  The results of Monte Carlo, our functional,
%%     and one previously published functional\cite{gross2009density,
%%       yu2002fmt-dft-inhomogeneous-associating} are compared in each
%%     case.  In the bottom panel we plot the density, computed with
%%     Monte Carlo and with DFT.}
%%   \label{fig:walls-10}
%% \end{figure}

@@

We simulate the inhomogeneous hard sphere fluid at four hard-wall
interfaces.  The first and simplest is a flat hard wall.  We
then study two convex hard surfaces.  One is an excluded sphere with
diameter $2\sigma$, which corresponds to a ``test particle''
simulation with one of a hard sphere at the origin with diameter
$\sigma$.  The
second is an excluded sphere with diameter $6\sigma$,
which demonstrates behavior typical of mildly convex hard surfaces.
Finally, we study a concave surface given by a hard cavity in which
our fluid is free to move up to a diameter of $8\sigma$, which
demonstrates behavior typical of mildly concave surfaces.  In each
case, we performed a low-density (filling fraction 0.1) and high-density
(filling fraction 0.4) simulation.  We performed additional
computations over a wider range of curvatures and densities, but
chose these as typical examples.

%% \begin{figure}
%%   \includegraphics[width=\columnwidth]{figs/inner-4-10}
%%   \caption{(Color online) Density and correlation function around a hard sphere with
%%     diameter the same as those in the fluid, with a bulk filling
%%     fraction of 0.1.}
%%   \label{fig:inner-4-10}
%% \end{figure}

@@

We begin by presenting our low-density results, corresponding to a
filling fraction of 0.1, which are shown in
Figure~\ref{fig:low-density}.  At this low density,
the contact value of the correlation function in the bulk is only 1.3,
indicating that correlations are indeed small and that the fluid should be
relatively easy to model.  Indeed, the contact density at the hard
surface is only around 50\% higher than the bulk, and the FMT
predicted density is close to indistinguishable from the true
density for each of the four configurations.

%% \begin{figure}
%%   \includegraphics[width=\columnwidth]{figs/inner-12-10}
%%   \caption{Density and correlation function around a hard sphere with
%%     an excluded diameter of $6\sigma$, with a bulk filling fraction of
%%     0.1.}
%%   \label{fig:inner-12-10}
%% \end{figure}

@@

%% \begin{figure}
%%   \includegraphics[width=\columnwidth]{figs/outer-16-01}
%%   \caption{Density and correlation functions near the surface of a
%%     spherical cavity with diameter $16\sigma$ at a bulk filling
%%     fraction of 0.1.}
%%   \label{fig:outer-10}
%% \end{figure}

@@

%% \begin{figure}
%%   \includegraphics[width=\columnwidth]{figs/walls-40}
%%   \caption{Density and correlation function at a hard wall with bulk
%%     filling fraction of 0.4.}
%%   \label{fig:walls-40}
%% \end{figure}

%% \begin{figure}
%%   \includegraphics[width=\columnwidth]{figs/inner-4-40}
%%   \caption{Density and correlation function around a hard sphere with
%%     diameter the same as those in the fluid, with a bulk filling
%%     fraction of 0.4.}
%%   \label{fig:inner-4-40}
%% \end{figure}

%% \begin{figure}
%%   \includegraphics[width=\columnwidth]{figs/inner-12-40}
%%   \caption{Density and correlation function around a hard sphere with
%%     an excluded diameter of $6\sigma$, with a bulk filling fraction of
%%     0.4.}
%%   \label{fig:inner-12-40}
%% \end{figure}

\begin{figure*}
  \noindent\includegraphics[width=0.8\textwidth]{figs/low-density}
  %% \noindent
  %% \begin{tabular}{cc}
  %%   (a)\includegraphics[width=8cm]{figs/walls-10} &
  %%   (c)\includegraphics[width=8cm]{figs/inner-4-10}\\
  %%   (b)\includegraphics[width=8cm]{figs/inner-12-10} &
  %%   (d)\includegraphics[width=8cm]{figs/outer-16-01}
  %% \end{tabular}
  \caption{ (Color online) Density and correlation function in systems
    with a ``low density'' bulk filling fraction of 0.1.  The
    subplots each show a different system: (a) next to a flat hard wall, (b)
    around a hard sphere with an excluded diameter of $6\sigma$, (c)
    around a hard sphere with an excluded diameter of $2\sigma$, and
    (d) within a spherical cavity with an included diameter of $8\sigma$.
    In the top and middle panels of each subfigure are the
    asymmetrically averaged correlation function $g_\sigma^A$ (defined
    in Equation~\ref{eq:gA}) and the symmetrically averaged
    correlation function $g_\sigma^S$ (defined in
    Equation~\ref{eq:gS}).  The results of Monte Carlo, our
    functional, and one previously published
    functional\cite{gross2009density,
      yu2002fmt-dft-inhomogeneous-associating} are compared in each
    case.  The bottom panels show the density computed with
    Monte Carlo and with DFT.}
  \label{fig:low-density}
\end{figure*}

\begin{figure*}
  \noindent\includegraphics[width=0.8\textwidth]{figs/high-density}
  %% \noindent
  %% \begin{tabular}{cc}
  %%   (a)\includegraphics[width=8cm]{figs/walls-40} &
  %%   (c)\includegraphics[width=8cm]{figs/inner-4-40}\\
  %%   (b)\includegraphics[width=8cm]{figs/inner-12-40} &
  %%   (d)\includegraphics[width=8cm]{figs/outer-16-04}
  %% \end{tabular}
  \caption{ (Color online) Density and correlation function in systems
    with a ``high density'' bulk filling fraction of 0.4.  The
    subplots each show a different system: (a) next to a flat hard wall, (b)
    around a hard sphere with an excluded diameter of $6\sigma$, (c)
    around a hard sphere with an excluded diameter of $2\sigma$, and
    (d) within a spherical cavity with an included diameter of $8\sigma$.
    In the top and middle panels of each subfigure are the
    asymmetrically averaged correlation function $g_\sigma^A$ (defined
    in Equation~\ref{eq:gA}) and the symmetrically averaged
    correlation function $g_\sigma^S$ (defined in
    Equation~\ref{eq:gS}).  The results of Monte Carlo, our
    functional, and one previously published
    functional\cite{gross2009density,
      yu2002fmt-dft-inhomogeneous-associating} are compared in each
    case.  The bottom panels show the density computed with
    Monte Carlo and with DFT.}
  \label{fig:high-density}
\end{figure*}

At a higher density corresponding to a filling fraction of 0.4,
correlations are much stronger, with the bulk contact value of the
correlation function of 3.7, as seen in
Figure~\ref{fig:high-density}.  This results in larger
oscillations in the density at the hard surfaces, and correspondingly
more interesting behavior in the correlation function near the
interface.  The density predicted by the White Bear functional agrees
reasonably well with the simulation results, although not so well as
it did at lower density.  The discrepancies are largest in the case of
the spherical cavity (Figure~\ref{fig:high-density}d), in which the DFT considerably underestimates the
range of the density oscillations.

The asymmetric version of the correlation function once again displays
relatively smooth behavior with a few small
oscillations near the interface, and a somewhat elevated value within
a diameter of the hard surface, with the magnitude of this elevation
somewhat different in each configuration.  As was the case at low
density, our correlation function $g_\sigma^A$ matches very closely
the Monte Carlo data, reproducing quite well the structure near the
interface in each configuration, although in the spherical cavity there is a small, but significant
discrepancy, comparable to the discrepancy found in the density
itself.  In each case, the correlation of Gross dramatically
underestimates the correlation at the interface, at one extreme by
40\% in the case of the spherical cavity, and at the other extreme by 15\%
in the test-particle scenario (Figure~\ref{fig:high-density}c).

%% \begin{figure}
%%   \includegraphics[width=\columnwidth]{figs/outer-16-04}
%%   \caption{Density and correlation functions near the surface of a
%%     spherical cavity with diameter $16\sigma$ at a bulk filling
%%     fraction of 0.4.}
%%   \label{fig:outer-40}
%% \end{figure}

The symmetrically averaged correlation function shows considerably
more structure near the interface at high density, and this structure
varies considerably depending on the curvature of the hard surface.
In each case, this structure is not reflected in the theoretical
predictions, neither that of this paper, nor that of Yu and
Wu~\cite{yu2002fmt-dft-inhomogeneous-associating}.  As was the case at
low density, both functionals give significant and finite values in
the region in which there are no contacts (Figures~\ref{fig:low-density}a), but at high density they
also miss the large oscillations that are present near the flat wall
and the concave surface (Figures~\ref{fig:high-density}a).  As was the case at low density, the
functional of Yu and Wu~\cite{yu2002fmt-dft-inhomogeneous-associating}
gives slightly better agreement with the simulation results than that
which we derive in Section~\ref{sec:g-S}.
